The Magnetorotational Instability Prefers Three Dimensions

### 2019-11-09 paper/paper.tex
Fixed URL for eigentools

Figure~\ref{fig:growth_rate}b compares the numerical growth rates for $\SSC=1.002$ between $0\le{k_{y}}\le0.2$ to the asymptotic approximation, showing good agreement where the latter is valid.
Figure~\ref{fig:growth_rate}c shows the full spectrum for $\SSC=1.002$.
The plot shows a purely growing/decaying complex-conjugate pair (orange/blue dots on the real axis) consistent with equation~(\ref{eq:asymp}).
The other stable modes (grey dots) are rotationally modified Alfv\'{e}n waves found in left- and right-going pairs, consistent with the analytic predictions for two-dimensional stability calculations.
We reject spurious eigenvalues by using \texttt{eigentools} \footnote{\protect\url{https://bitbucket.org/jsoishi/eigentools}} to solve equations~(\ref{eq:mhd}-\ref{eq:divu}) at two resolutions and retain only pairs equal to within one part in $10^{-6}$.

>>>>

Figure~\ref{fig:growth_rate}b compares the numerical growth rates for $\SSC=1.002$ between $0\le{k_{y}}\le0.2$ to the asymptotic approximation, showing good agreement where the latter is valid.
Figure~\ref{fig:growth_rate}c shows the full spectrum for $\SSC=1.002$.
The plot shows a purely growing/decaying complex-conjugate pair (orange/blue dots on the real axis) consistent with equation~(\ref{eq:asymp}).
The other stable modes (grey dots) are rotationally modified Alfv\'{e}n waves found in left- and right-going pairs, consistent with the analytic predictions for two-dimensional stability calculations.
We reject spurious eigenvalues by using \texttt{eigentools} \footnote{\protect\url{https://github.com/dedalusproject/eigentools}} to solve equations~(\ref{eq:mhd}-\ref{eq:divu}) at two resolutions and retain only pairs equal to within one part in $10^{-6}$.
